Painting with Triangles

### 2014-04-21 paper.tex
Updated figures and captions
fixing citations

Previous work has focused on converting images into vector graphics to take advantage of the
efficient storage, easy editing, and infinite resolution it provides. For example \cite{lecot:ARD:2006}
minimizes an energy function to segment an image into a number of regions that are bounded
by cubic splines and filled with solid colors or gradients. A different approach by \cite{Lai:2009:ATG:1531326.1531391} 
automatically creates gradient meshes with support for holes. Yet another example is \cite{10.1109/TVCG.2012.76} 
which converts an image into a triangle mesh. All three of these can convert images into
a vector representation, yet none of them allow a user to create a painting in the vector medium.

Other work has proposed novel vector graphic data structures. For example \cite{Frisken:2000:ASD:344779.344899}
defines Adaptively Sampled Distance Fields (ADF). ADFs specify a signed distance function to a surface.
Rendering the shape requires sampling the function to determine whether or not a pixel is on the surface.
A quadtree accompanies the distance function to specify where higher sampling rates are necessary. \cite{Bremer:2001:VCM}
further describes how ADFs can be created and used. However, it is unclear how ADFs might be used in a general
painting program where strokes with solid colors and gradients are composited on top of one another.

@@

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcs2}
    \caption{An example of color arcs. The orange lines are boundary edges. Black lines form the triangle
    mesh with the boundary edges. Each point is given a color arc which defines its color in that range.
    Note that the points in the middle row have different colors on top and bottom. This gives blue
    triangles on top and red on bottom with a hard boundary in between.}
    \label{fig:arcs}
\end{figure}

@@

\begin{figure}
    \centering
        \includegraphics[width=.2\textwidth]{images/intersectioncolorarcs1new}
        \includegraphics[width=.2\textwidth]{images/intersectioncolorarcs2new}

    \caption{Left: A blue stroke is composited over a red stroke. Point A is covered
             by the the blue stroke and point B is on top of the red stroke. Middle:
             New color arcs are determined. Both of A's color arcs are composited
             with the blue stroke which turns red to purple and transparent to blue. Similarly
             both of B's color arcs are composited on top of the red stroke which turns
             blue to purple and transparent to red. Two intersection points C and D are
             added. Their color arcs are determined by examining neighboring points. Right: 
             A new triangle mesh is generated to preserve boundaries. Note that triangles
             in the intersection will be purple.}
    \label{fig:intersectioncolors}
\end{figure}

\begin{figure*}
    \centering
        \includegraphics[width=.32\textwidth]{images/composite1new}
        \includegraphics[width=.32\textwidth]{images/composite2new}
        \includegraphics[width=.32\textwidth]{images/composite3new}
    \caption{Left: A blue stroke is composited over a red stroke. Point A is covered
             by the the blue stroke and point B is on top of the red stroke. Middle:
             New color arcs are determined. Both of A's color arcs are composited
             with the blue stroke which turns red to purple and transparent to blue. Similarly
             both of B's color arcs are composited on top of the red stroke which turns
             blue to purple and transparent to red. Two intersection points C and D are
             added. Their color arcs are determined by examining neighboring points. Right: 
             A new triangle mesh is generated to preserve boundaries. Note that triangles
             in the intersection will be purple.}
    \label{fig:colorarcdeterminer}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.3\textwidth]{images/stop1}
        \includegraphics[width=0.3\textwidth]{images/stop2}
        \includegraphics[width=0.3\textwidth]{images/stop3}
    \caption{Another painting by an artist, using soft and hard strokes at a variety of scales.  Middle and right images are zoomed in.}
    \label{fig:stop}
\end{figure*}

>>>>

Previous work has focused on converting images into vector graphics to take advantage of the
efficient storage, easy editing, and infinite resolution it provides. For example the method of
Lecot and L\'{e}vy~\shortcite{lecot:ARD:2006}
minimizes an energy function to segment an image into a number of regions that are bounded
by cubic splines and filled with solid colors or gradients. A different approach by \cite{Lai:2009:ATG:1531326.1531391} 
automatically creates gradient meshes with support for holes. Yet another example is \cite{10.1109/TVCG.2012.76} 
which converts an image into a triangle mesh. All three of these can convert images into
a vector representation, yet none of them allow a user to create a painting in the vector medium.

Other work has proposed novel vector graphic data structures. For example 
Frisken~\etal~\shortcite{Frisken:2000:ASD:344779.344899}
introduced Adaptively Sampled Distance Fields (ADFs), which specify a signed distance function to a surface in 3D
(or a curve in the plane).
%
Rendering the shape requires sampling the function to determine whether or not a pixel is on the shape.
A quadtree accompanies the distance function to specify where higher sampling rates are necessary. \cite{Bremer:2001:VCM}
further describes how ADFs can be created and used. However, it is unclear how ADFs might be used in a general
painting program where strokes with solid colors and gradients are composited on top of one another.

@@

\begin{figure}
    \centering
        \includegraphics[width=0.4\textwidth]{images/colorarcsfinal}
    \caption{An example of color arcs. The orange lines are boundary edges. Black lines form the triangle
    mesh with the boundary edges. Each point is given a color arc which defines its color in that range.
    Note that the points in the middle row have different colors on top and bottom. This gives blue
    triangles on top and red on bottom with a hard boundary in between.}
    \label{fig:arcs}
\end{figure}

@@

\begin{figure}
    \centering
        \includegraphics[width=.2\textwidth]{images/intersectioncolorarcs1final}
        \includegraphics[width=.2\textwidth]{images/intersectioncolorarcs2final}

    \caption{Left: A red stroke is composited over a blue stroke. An intersection
            point is inserted in the center and four color arcs must be determined. Right:
            The four colors are resolved as the four combinations of the red stroke's color
            arcs composited over the blue stroke's color arcs.}
    \label{fig:intersectioncolors}
\end{figure}

\begin{figure*}
    \centering
        \includegraphics[width=.32\textwidth]{images/composite21}
        \includegraphics[width=.32\textwidth]{images/composite22}
        \includegraphics[width=.32\textwidth]{images/composite23}
    \caption{Left: A blue stroke is composited over a red stroke. Point A is covered
             by the the blue stroke and point B is on top of the red stroke. Middle:
             New color arcs are determined. Both of A's color arcs are composited
             with the blue stroke which turns red to purple and transparent to blue. Similarly
             both of B's color arcs are composited on top of the red stroke which turns
             blue to purple and transparent to red. Two intersection points C and D are
             added. Their color arcs are determined by examining neighboring points. Right: 
             A new triangle mesh is generated to preserve boundaries. Note that triangles
             in the intersection will be purple.}
    \label{fig:colorarcdeterminer}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=0.3\textwidth]{images/stop12}
        \includegraphics[width=0.3\textwidth]{images/stop22}
        \includegraphics[width=0.3\textwidth]{images/stop32}
    \caption{Another painting by an artist, using soft and hard strokes at a variety of scales.  Middle and right images are zoomed in.}
    \label{fig:stop}
\end{figure*}
